A Study on Neural Models for Target-Based Computer-Assisted Musical Orchestration

### 2020-10-06 paper/aimusic2020/paper.tex
Rephrase CAC quote

Target-based computer-assisted orchestration can be thought of as the process of searching for the best combinations of sounds in a database of instrumental samples, to match a target sound under a specific similarity metric and specific sets of constraints. A solution to this problem is a set of orchestral scores that represent the mixtures of audio samples in the database, ranked by similarity with the target sound.

>>>>

Target-based computer-assisted orchestration takes a target sound as an input and attempts to find instrumental samples that best match the target given a specific similarity metric and a set of constraints. A solution to this problem is a set of orchestral scores that represent the mixtures of audio samples in the database, ranked by similarity with the target sound.
